\showyourwork: a workflow for open source scientific articles

### 2021-12-20 src/ms.tex
working on paper

% Filler text
\usepackage{blindtext}

@@

% Abstract with filler text
\begin{abstract}
    \blindtext
\end{abstract}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
        \caption{
            LEGWORK plot. Figure reproduced from \citet{Wagg2021}.
        }
        \label{fig:eccentricity}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/rossbyridge.pdf}
        \caption{
            Rossby ridge. Figure reproduced from David et al. (in prep).
        }
        \label{fig:rossbyridge}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
        \caption{
            Caption. Figure adapted from \citet{Luger2021}; data originally from \citet{Crossfield2014}.
        }
        \label{fig:luhman16b}
    \end{centering}
\end{figure}

@@

\begin{figure*}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/dag.pdf}
        \caption{
            A directed acyclic graph (DAG) showing the build process for each of the (other) figures in this article. 
        }
        \label{fig*:dag}
    \end{centering}
\end{figure*}

>>>>

\usepackage{listings}

\lstdefinestyle{LaTeX}{%
    language=[LaTeX]TeX,
    basicstyle=\ttfamily\footnotesize,
    texcsstyle=*\bf\color{black},
    numbers=none,
    breaklines=true,
    commentstyle=\color{red},
    frame=single,
    tabsize=2,
    keywords={begin,caption,label,end,includegraphics},   
}

@@

% Abstract with filler text
\begin{abstract}
    Abstract coming soon.
\end{abstract}

@@

Introduction coming soon.

\section{Inferring the figure tree}

\showyourwork determines the relationship between a figure (e.g., a \texttt{*.pdf} image) and the script that generated it (e.g., a \texttt{*.py} file) via inspection of the \texttt{figure} environment in the \texttt{TeX} file. 
Specifically, it inspects the \texttt{{\textbackslash}includegraphics} and \texttt{{\textbackslash}label} commands to infer the name of the figure and the script that generated it, respectively.
Consider the following snippet, used to generate Figure~\ref{fig:eccentricity}:
%
\begin{lstlisting}[
    style=LaTeX,
    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
    emph={figures/eccentricity.pdf,fig:eccentricity},
    emphstyle={\color{blue}}
]
\begin{figure}
  \begin{centering}
    \includegraphics{figures/eccentricity.pdf}
    \caption{...}
    \label{fig:eccentricity}
  \end{centering}
\end{figure}
\end{lstlisting}

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
        \caption{
            The effect of eccentricity on the detectability of a \emph{LISA} source; reproduced from Figure 3 in \citet{Wagg2021}.
        }
        \label{fig:eccentricity}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/luhman16b.pdf}
        \caption{
            16 \emph{CRIRES} spectra of WISE 1049-5319B spanning a full rotation period of the brown dwarf; adapted from Figure 14 in \citet{Luger2021}. 
            Data originally from \citet{Crossfield2014}.
        }
        \label{fig:luhman16b}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/rossbyridge.pdf}
        \caption{
            A pile-up of stars in the rotation period-temperature space at slightly faster rotation than the sun (orange dot); adapted from Figure 1 in David et al. (in prep).
        }
        \label{fig:rossbyridge}
    \end{centering}
\end{figure}

@@

\begin{figure*}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/dag.pdf}
        \caption{
            A directed acyclic graph (DAG) showing the build process for each of the (other) figures in this article. 
            Figure scripts are represented by black rectangles; helper scripts (such as ones imported by figure scripts or used in dataset generation) are similar, but have rounded edges.
            Blue cylinders correspond to Zenodo records; blue boxes correspond to datasets.
        }
        \label{fig*:dag}
    \end{centering}
\end{figure*}
